Data Management for LSST Special Programs

### 2024-03-26 sec_sci.tex
update region labels

\textbf{Region Labels -- } 
Based on Right Acension and Declination.
To be applied to data by Rubin Data Management, e.g., using a look-up table.
Region labels would include, e.g., WFD low-dust, Galactic Plane, Galactic 
Bulge, SCP, NES, or Virgo; DDF fieldname; mini-survey region name.
Region labels should be propagated to processed images (visit, 
difference, and deep coadds), catalog sources, and catalog static-sky objects.
A given image might have more than one region label due to overlaping regions,
but they could be, e.g., held in a single string as a CSV.

>>>>

\textbf{Region Labels -- } 
Applied to a visit based on its Right Acension and Declination.
To be applied to data by Rubin Data Management using, e.g., a look-up table.
Region labels would include, e.g., WFD low-dust, Galactic Plane, Galactic 
Bulge, SCP, NES, or Virgo; DDF fieldname; mini-survey region name.
A given visit is likely to have multiple region labels because, for example,
the DDFs are within the WFD low-dust region.
These could be stored in, e.g., a single string as a CSV.

The region labels should be available to users as query constraints for
all images and tables, via both the butler and the TAP service, but otherwise
the details of region label implementation are left to Rubin Data Management.

For example, for images, the region labels could be propagated to processed images
(e.g., visit, difference, and deep coadds), so that users may query the ObsTAP 
service for all images with a given region label.
For catalogs, the region labels could be stored for individual sources and
objects as a table column, or for TAP-accessible tables stored in a joinable
table such as the Visit, ccdVisit, or coaddPatches tables.
Another option may be to map regions into spatial divisions (htm or healpix),
and enable users to query image and catalog products via their htm.
